\part{Packet decode functions}
Includes functions for receiving and decoding packets from XBee through UART.

\section{Receive packet (rxpacket)}
Read the UART buffer for an XBee API frame. Checks the frame for length and checksum and returns the payload sans headers and checksum.
\subsection{Returns:}
\begin{enumerate}
\item success - (type: Integer) Returns a 1 for a successful read, 0 otherwise.
\item payload - (type: Bytes) XBee API frame payload.
\end{enumerate}
\subsection{Arguments:}
\begin{enumerate}
\item ser - Serial interface returned from serial.Serial() function of pyserial.
\end{enumerate}

\section{Decode AT Command Response (decode\_atcomres)}
Decodes AT Command Response (frame 0x88)payload from rxpacket(). Prints the following decoded fields to the console:
\begin{itemize}
\item Frame ID
\item AT Command
\item Command Status
\item Command Data (if available)
\end{itemize}
\subsection{Returns:}
\begin{enumerate}
\item error - (type: Integer) Returns a 0 when the status field of the received packet is 0 ('OK'). Returns 1 otherwise.
\end{enumerate}
\subsection{Arguments:}
\begin{enumerate}
\item payload - (type: Bytes) XBee frame sans headers and checksum.
\end{enumerate}

\section{Decode Transmit Status (decode\_txstat)}
Decodes Transmit Status (frame 0x8b) payload from rxpacket(). Prints the following decoded fields to the console:
\begin{itemize}
\item Frame ID
\item 16-bit Destination Address
\item Transmit Retry count
\item Delivery status
\item Discovery status
\end{itemize}
\subsection{Returns:}
\begin{enumerate}
\item error - (type: Integer) Returns a 0 when the delivery status field of the received packet is 0 ('OK'). Returns 1 otherwise.
\end{enumerate}
\subsection{Arguments:}
\begin{enumerate}
\item payload - (type: Bytes) XBee frame sans headers and checksum.
\end{enumerate}

\section{Decode Received Packet (decode\_rxpacket)}
Decodes a received packet (frame 0x90) payload from rxpacket(). Prints the following decoded fields to the console:
\begin{itemize}
\item 64-bit source address
\item Reserved field
\item Receive Options
\item Received Data
\end{itemize}
\subsection{Returns:}
None
\subsection{Arguments:}
\begin{enumerate}
\item payload - (type: Bytes) XBee frame sans headers and checksum.
\end{enumerate}

\section{Decode Payload (decode\_payload)}
Parses the first byte of a payload and calls the appropriate decoding function. Currently supports the following XBee API frame types:
\begin{itemize}
\item AT Command Response (0x88)
\item Transmit Status (0x8b)
\item Received Packet (0x90)
\end{itemize}
\subsection{Returns:}
\begin{itemize}
\item status - (type: Integer) forwards returns of decode\_atcomres() and decode\_txstat(). Returns 0 otherwise.
\end{itemize}
\subsection{Arguments:}
\begin{itemize}
\item payload - (type: Bytes) XBee frame sans headers and checksum
\end{itemize}

\part{Packet Decode with logging}
Decode functions which log to a file.

\section{Decode Generic Payload (decodelog\_payload)}
Decodes a generic payload and logs decoded fields to a file. Currently supports the following frames:
\begin{itemize}
\item Received packet (0x90)
\end{itemize}
The function prints a line (to a file) in the format "[f1] Raw: 0x [f2]" with the following fields:
\begin{enumerate}
\item Timestamp [f1]
\item Raw payload in bytes [f2]
\end{enumerate}
The function then calls the corresponding decoding function that may print further parsed fields from the raw packet.

\subsection{Returns:}
None
\subsection{Arguments:}
\begin{enumerate}
\item fp - (type: File pointer) Output log file.
\item payload - (type: Bytes) XBee frame sans headers and checksum.
\end{enumerate}

\section{Decode Receive Packet (decodelog\_rxpacket)}
Decodes a receive packet frame (0x90). The function prints a line (to a file) in the format "---- 90, [f1], [f2], [f3], [f4]" with the following fields:
\begin{enumerate}
\item 64-bit source address in hexadecimal [f1]
\item Reserved field in hexadecimal [f2]
\item Receive options in hexadecimal [f3]
\item Received data in hexadecimal [f4]
\end{enumerate}
\subsection{Returns:}
None
\subsection{Arguments:}
\begin{enumerate}
\item fp - (type: File pointer) Output log file.
\item payload - (type: Bytes) XBee frame sans headers and checksum.
\end{enumerate}